The Evolution of Phenotypically Invariant Genetic Networks

### 2017-08-04 kalman_walk_paper.tex
another small note

Then, $\hat A \to A + \epsilon X$  does
$$\begin{aligned}
    A \to A + \epsilon P^{-1} X P 
\end{aligned}$$
and $\hat B \to B + \epsilon Y$ does
$$\begin{aligned}
    B \to B + \epsilon P^{-1} Y
\end{aligned}$$
and $\hat C \to C + \epsilon Z$ does
$$\begin{aligned}
    C \to C + \epsilon Z P .
\end{aligned}$$
These degrees of freedom depend on $P$, but both through the change of basis $P$
and the form of allowable $X$, $Y$, and $Z$.

This gives us an upper bound on the number of degrees of freedom.
\plri{maybe? depending on if choice of $P$ affects anything.}
However, some of these may be redundant.
For instance, changing $P$ in the direction of 
a $Q$ that satisfies both $A P^{-1} Q = P^{-1} Q A$ and $C P^{-1} Q = 0$
is equivalent to changing $B$ by $Y = QB$.

>>>>

Then, $\hat A \to A + \epsilon X$  does
$$\begin{aligned}
    A \to A + \epsilon P^{-1} X P 
\end{aligned}$$
and $\hat B \to B + \epsilon Y$ does
$$\begin{aligned}
    B \to B + \epsilon P^{-1} Y
\end{aligned}$$
and $\hat C \to C + \epsilon Z$ does
$$\begin{aligned}
    C \to C + \epsilon Z P .
\end{aligned}$$
These degrees of freedom look like they depend on $P$, 
which is not unique,
but for any two choices of $P$ there are corresponding choices of $X$
that give the same actual change in $A$ (and likewise for $Y$ and $Z$).

Therefore, this gives us an upper bound on the number of degrees of freedom,
in terms of the dimensions of the blocks in the Kalman decomposition ($n_\ro$ etc)
and the dimensions of $B$ and $C$ ($n_B$ and $n_C$ respectively):
namely, for $W$, $X$, $Y$, and $Z$ respectively:
$$\begin{aligned}
    n^2 
    + (n_{\rno} + n_\ro n_\nro + n_\nrno(n_\nrno + n_\nro) + n_\nro^2)
    + n_B n_\rno
    + n_C n_\nrno .
\end{aligned}$$
However, some of these may be redundant.
For instance, changing $P$ in the direction of 
a $Q$ that satisfies both $A P^{-1} Q = P^{-1} Q A$ and $C P^{-1} Q = 0$
is equivalent to changing $B$ by $Y = QB$.
